Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-28 GWLDCII.tex
a few comments

On both of the last two points, we differ from the standard convention in the physics literature, where propagators are written as ordered pairs $(i,j)$ with $1 \leq i<j \leq n$.  Additionally, note that in this paper, we allow for the propagator set $\cP$ to be empty. This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
\hlfix{}{I changed the last three paragraphs a certain amount more on account of referee M's comments 3 and 4 -- we should discuss it.}

@@

The first condition bounds the total number of propagators in the diagram, while the second limitshow  densely  propagators  can  be  fitted  into  any  part  of  the  diagram.  The third condition simply requires that propagators are non-crossing.

>>>>

On both of the last two points, we differ from the standard convention in the physics literature, where propagators are written as ordered pairs $(i,j)$ with $1 \leq i<j \leq n$.  Additionally, note that in this paper, we allow for the propagator set $\cP$ to be empty. This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
\hlfix{}{I changed the last three paragraphs a certain amount more on account of referee M's comments 3 and 4 -- we should discuss it.} \sanote{should we make a comment about propagators being multisets here (in addition to changes below)? I remember parallel edges being bad being news to Lionel when I wrote the original paper.}

@@

The first condition bounds the total number of propagators in the diagram, while the second limits how  densely  propagators  can  be  fitted  into  any  part  of  the  diagram.  The third condition simply requires that propagators are non-crossing.
